---
title: "Synthetic Sales Data Analysis"
author: "Maryama"
date: "2026-10-02"
output: html_document
---

> **AI Assistance Declaration:** I used ChatGPT (GPT-5.6 Sol) for planning, formatting, and improving the R Markdown documentation. Prompts used are documented in `Appendix_AI_Prompts.md`. I verified the output by knitting the document in Posit Cloud and checking that the headings, R code, and results rendered correctly. All final calculations are done by myself. I am responsible for the accuracy and originality of this work.
# Purpose

This R Markdown document explains an R script that analyzes a synthetic sales dataset. The script creates sales data for four regions, displays the data, and summarizes total sales by region.

## Inputs

The script uses a synthetic dataset with two variables:

- **Region:** North, South, East, and West
- **Sales:** Sales values for each region

```{r}
sales_data <- data.frame(
  Region = c("North", "South", "East", "West"),
  Sales = c(12000, 15000, 11000, 17000)
)

print(sales_data)
```

## Outputs

The script calculates total sales for each region using the `aggregate()` function.

```{r}
sales_by_region <- aggregate(Sales ~ Region, data = sales_data, sum)

print(sales_by_region)
```

The output shows the total sales for the North, South, East, and West regions.
